---
# output: pdf_document
output: github_document
bibliography: references.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# reproducibleCoursework

reproducibleCoursework is a folder containing everything you need to ensure your coursework is reproducible.

## How it works

Reproducibility is essential for science.
Saving your work as an RMarkdown (.Rmd) file enables others to replicate what you have done.
RMarkdown files are special:
this `README.Rmd` file, for example, allows you to include R chunks like so:

```{r cars}
summary(cars)
```

Another great thing about `.Rmd` files is they can produce a range of outputs.
This file can be converted to a PDF document, for example, by replacing `output: github_document` with `output: pdf_document` at the top of the document.

Test it out by following these steps:

- Download the template folder from https://github.com/ITSLeeds/reproducibleCoursework/archive/master.zip
- Unzip it somewhere sensible on your computer
- Open the project in RStudio by double-clicking on `reproducibleCoursework.Rproj` in a browser or via File > Open in RStudio; you must have R and RStudio installed, see [Efficicient R Programming for more on this](https://csgillespie.github.io/efficientR/efficient-set-up.html) [@gillespie_efficient_2016]
- Open and edit the file `README.Rmd`, e.g. by entering `file.edit("README.Rmd")`
- 'Knit' the results, by clicking on the 'Knit' button or pressing `Ctl-Shift-K` in RStudio or executing the following command:

```{r, eval=FALSE}
knitr::knit("README.Rmd")
```

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

If you want your work to be visible to others online, don't forget to commit and push the resulting figure files, so they display on GitHub!

You can add citations easily to the `references.bib` file, in .bib format.

Read more about the RMarkdown file format here: https://rmarkdown.rstudio.com/


## Folder structure

Code lives in the `code` folder and minimal example datasets live in the folder `minimal-example-data`.
Only small datasets are kept in the repo to avoid mixing code and data.
Larger datasets should be hosted elsewhere, e.g. on GitHub via the **piggyback** package.

## A simple example

Let's explore road crashes in Leeds.

## References
